%! Author = garance
%! Date = 10/21/25

% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage[toc,page]{appendix}
\usepackage{caption}
\usepackage{soul}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage{enumitem} % Pour personnaliser les listes

% Document
\begin{document}

    \title{
        { \textbf{Security Protocols and Verification}} \\[1ex]
        {\small Defense of Cryptographic Protocol}
    }


    \author{
        Garance Frolla \\
        Ely Marthouret \\
        Ewan Decima\\ \\
        Team: \textbf{ASKO OM8464A2}
    }

    \date{September / November 2025}


    \maketitle
    \tableofcontents
    \newpage

    \section{Attack from PCI-2690}
    
    \subsection{Second Refutation: Nonce Reuse Detection}

    Concerning the step \textbf{4.3. 5.} of your attack, even if the first refutation were ignored, your attack fails due to the protocol's specifications regarding nonce reuse.
    
    \begin{enumerate}[label=\arabic*., start=5]
        \item \textbf{Bob B}: B receives Msg 3 from S at $t_{rejeu}$.
        \item B decrypts the message with his key $K_{BS}$ and extracts $K_{AB}$ and $\tau$.
        \item B verifies: $t_{rejeu} \geq \tau + \lambda$? This is false.
        \item B accepts the message and uses the old key $K_{AB}$ to decrypt Msg 1 (replayed by Eve) and obtains the \textbf{old nonce $N_A$}.
    \end{enumerate}

    At this point, as stated in the protocol's description:
    \begin{itemize}
        \item \enquote{B checks also the validity of the first message}
        \item \enquote{All agents can detect if a nonce has been reused. If an agent detects that a nonce is reused, the agent aborts.}
    \end{itemize}
    
    Since Bob ($B$) has obtained the \textbf{old nonce $N_A$}, he detects a \textbf{nonce reuse} (the nonce from the replayed Msg 1 is a nonce from a previous, completed session).
    
    \paragraph{}
    Therefore, \textbf{Bob immediately aborts the session}. Alice ($A$), not receiving any response ($B \rightarrow A$: Msg 4) in the expected time frame, will also consider the protocol to have been aborted. The attack fails at this step.


    \section{Conclusion}
    We \underline{refuse this attack}, but we are ready to face another one.

\end{document}
